---
title: "Lab 1: Introduction to Quarto"
author: "Parker Mascott"
date: "09/29/2024"
format:
  html:
    code-fold: true
    toc-title: "Table Of Contents"
    toc: true
    toc-expand: 2
editor: source
embed-resources: true
execute:
  echo: true
  error: true

---

# Part Two: Exploring Quarto Documents

## Specifying Global Execute Options

Execution options specify how the R code in your Quarto document should be
displayed. This [guide](https://quarto.org/docs/computations/execution-options.html)
provides descriptions on the options you can specify in a document's execution.

**Question 1** -- Add your name and the date to the YAML. 

**Question 2** -- Add an `execute` line to your YAML that includes the following
options, (1) your source code is always output on the page, and (2) your
document will render even if there are errors.

## Loading and Viewing the Tooth Growth Dataset

```{r}
# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)

```

**Question 3** -- Let's spice this code up a bit. Delete `1 + 1` from the code
chunk and paste in the code provided in the Lab 1 instructions. 

### Check the Data Documentation

**Question 4** -- In your **console** (*not* in the Quarto document), type
`?ToothGrowth` (or alternatively `help(ToothGrowth)`.Use the information that
pops up in the *Help* pane in RStudio to fill in the blanks below. 

*This dataset investigates the effect of Vitamin C on tooth growth in Guinea Pigs.*

*The two supplement delivery methods include OJ (orange juice) and VC (ascorbic acid).*

*`ToothGrowth` is a data frame with 60 observations and 3 variables.*

**Question 5** -- *Before* the code chunk, change the "Running the Provided
Code" section header to a header that better describes the contents of this
section (e.g., Tooth Growth Dataset).

## Creating a Plot

**Question 6** -- Replace the `plot(pressure)` code with the code provided in the Lab 1 instructions.

```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 2
#| fig-cap: 
#|   - "Box Plot 1"
#|   - "Box Plot 2"
#| fig-align: center


library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", y = "Length of Teeth (mm)")

ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", y = "Length of Teeth (mm)")


```

Now, run this code chunk! You should see two side-by-side boxplots, one plot
comparing tooth length between the two supplement delivery methods and one plot
comparing tooth length between the three different dosages uses. 

**Question 7** -- Read over the [Quarto documentation on figure options](https://quarto.org/docs/authoring/figures.html#computations)
and add an option (`#|`) to the above code chunk to make the figures print
side-by-side (i.e., in one row) in the rendered HTML file. 

**Question 8** -- Specify in the code chunk options that these boxplots 
should be **center aligned**.

**Question 9** -- Specify a **figure caption** for the boxplots (using a
code-chunk option).

Done!


## Conducting a t-test for ToothGrowth Dataset (Two Independent Samples)

Null: The treatment mean tooth length for the OJ supplement delivery method is the same as the treatment mean tooth length for the VC supplement delivery method.

Alternative: The treatment mean tooth length for the OJ supplement delivery method is different from the treatment mean tooth length for the VC supplement delivery method.

Assume unequal variances and a two-sided alternative.(var.equal = FALSE, alternative = "two-sided")

**Question 10**

```{r}
glimpse(ToothGrowth)

t.test(len ~ supp, data = ToothGrowth, var.equal = FALSE, alternative = "two.sided")

```
**Question 12** Findings

1. Our P-value of 0.06063 is slightly greater than 0.05. This results in us failing to reject the null hypothesis, concluding that there is not enough evidence for the treatment mean tooth length for the OJ supplement delivery method is different from the treatment mean tooth length for the VC supplement delivery method.

2. Our 95% confidence interval is from -0.171 to 7.571. This interval includes 0 which suggests that there might not be a significant difference in mean tooth length across treatments.

